Phenotype and risk assessment of insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-10-16 analysis/paper/paper.Rmd
fig 1 from vertical to horizontal

Due to a large number of documented reactions in the European Anaphylaxis Registry - we were able to match the VIA with non-VIA cases according to sex and age to reduce the comparison bias. 
When we analyzed a density plot of VIA cases according to age - we determined a bimodal distribution forming two subsets of patients with a cutoff age of 22 (Fig \@ref(fig:flow)B). Subsequently, we compared the management in both groups and matched the control group according to the severity of a reaction. Propensity score matching has been performed using the "MatchIt" package for R [@matchit]. The results of the propensity score matching are in Fig. \@ref(fig:flow)B-D and supplementary Fig \@ref(fig:matchingresult).

@@

```{r flow,fig.width=5.2,fig.height=6, fig.cap=" A) Flow-diagram illustrating the rationale for case inclusion and exclusion from the final analysis. B, C, D: Age, sex, and severity distribution was matched in cases in both groups to allow for comparable results between VIA and non-VIA cases. Two age-subsets of patients could be recognized based on the density plot of age (B)."}
ggarrange(ggplot()+
            background_image(png::readPNG("../figures/flow.png")),
          lower_panel,
          ncol = 1,
          nrow = 2,
          heights = c(1,0.4),
          labels = c("A","")
)
```

>>>>

Due to a large number of documented reactions in the European Anaphylaxis Registry - we were able to match the VIA with non-VIA cases according to sex and age to reduce the comparison bias. 
When we analyzed a density plot of VIA cases according to age - we determined a bimodal distribution forming two subsets of patients with a cutoff age of 22 (Fig. \@ref(fig:flow)B). Subsequently, we compared the management in both groups and matched the control group according to the severity of a reaction. Propensity score matching has been performed using the "MatchIt" package for R [@matchit]. The results of the propensity score matching are in Fig. \@ref(fig:flow)B-D and supplementary Fig \@ref(fig:matchingresult).

@@

```{r flow,fig.width=7,fig.height=4.5, fig.cap=" A) Flow-diagram illustrating the rationale for case inclusion and exclusion from the final analysis. B, C, D: Age, sex, and severity distribution was matched in cases in both groups to allow for comparable results between VIA and non-VIA cases. Two age-subsets of patients could be recognized based on the density plot of age (B)."}
ggarrange(ggplot()+
            background_image(png::readPNG("../figures/flow.png")),
          lower_panel,
          ncol = 2,
          nrow = 1,
          widths = c(1,0.5),
          labels = c("A","")
)
```
